---
title: "Lab 1: Intro to R"
author: "Yina Qiao"
date: "2023-02-02"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
```


```{R view data}
arbuthnot
```

```{r summary}
glimpse(arbuthnot)
```

```{r}
arbuthnot$boys
```
### Exercise 1

```{r view-girls-counts}
arbuthnot$girls
```


### Exercise 2

Insert any text here.

```{r}
ggplot(data = arbuthnot, aes(x = year, y = girls)) + 
  geom_point()
```
#### the plot above shown there is an increase in the number of girls being baptized from 1629 to 1710

### Exercise 3


```{r }

arbuthnot<-arbuthnot %>%
  mutate(total=boys+girls)
arbuthnot<-arbuthnot %>%
  mutate(boys_to_girls_ratio=boys/total)
arbuthnot<-arbuthnot %>%
  mutate(boy_ratio=boys/total)
ggplot(data=arbuthnot,aes(x=year,y=boy_ratio))+geom_line()

```
#### it looks like propotions of boys baptized are dropping gradually overtime.

### Exercise 4


```{r}
data('present', package='openintro')
glimpse(present)
```


### Exercise 5



```{r }
present<-present %>%
  mutate(total=boys+girls)
head(present)
head(arbuthnot)

```
#### The values in present dataset are much bigger than arbuthnot by 3 orders of magnitude

### Exercise 6


```{r }
present<-present %>%
  mutate(total=boys+girls)
present<-present %>%
  mutate(boys_to_girls_ratio=boys/girls)
present<-present %>%
  mutate(boys_ratio=boys/total)
ggplot(data = present, aes(x=year,y=boys_ratio))+geom_line()
```
#### the boy_ratio is decreasing over time for the present data, different from Arbuthnot's observation.

### Exercise 7


```{r }
present %>%
  arrange(desc(total))
```

